Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (7)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We agree with the reviewer that we could further improve the explanation of our study. In our manuscript, we compare model checking with software simulation. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in Section \textcolor{red}{"1 Introduction"}.

When we work with waveform, we are performing \textcolor{red}{testing or simulation}, and that is different of automated verification. \textcolor{red}{We consider that this demand (number 7 in this Reply Letter) is related to the experimental question done by the same reviewer at item number (6). Therefore we expect that the explanations done at item 6, with the consequent updated paper can cover any further issue about it}. 
\end{resposta}
\end{quote}

>>>>

We agree with the reviewer that we could further improve the explanation of our study. In our manuscript, we compare model checking with software simulation. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in Section 1 (Introduction).

When we work with waveform, we are performing testing or simulation, and that is different of automated verification. We consider that this comment (number $7$ in this Reply Letter) is related to the experimental question done by the same reviewer in (6). As a result, we expect that the explanations given in (6), together with the consequent updated manuscript, can cover any further concerns about this particular issue. 
\end{resposta}
\end{quote}
